NMRlipids Databank: Overlay Databank of Lipid Membrane Simulations Arising from Open Collaboration

### 2022-05-09 Manuscript/main.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width = 180mm]{Figures/overlay.pdf}
    \caption{a) Structure of a overlay databank. 
    %Raw data is available from a publicly accessible repository (layer 1).
    %The core of the databank contains information on the location of the raw data and indexing of molecular %compositions and simulation details described with universal naming conventions (layer 2).
    %The content of databank can be viewed and analysed using external programs that automatically read the information and data from layers 1 and 2 (layer 3). Examples of such applications are the GitHub repository generating the results presented in this work and the graphical access to the databank.
    More detailed structure of the layer 2 is illustrated in Fig.~\ref{DatabankStructure} in the SI.
    b) Distribution of lipids that are present in more than two trajectories in the databank.
    Lipids occuring in 1-2 trajectories are: DCHOL(2), DDOPC(2), DOPE(2), DEPC(1), DMPC(1), SAPI(1), POPI(1), SLPI(1), DLIPC(2), DSPC(2), DPPG(2), DPPE(1), and DLPC(1).
    c) Distribution of force fields used in the simulations.
    d) Distribution of the lengths of the trajectories, total number of trajectories and total lenght of the simulations.
    e) Currently available binary mixtures in the databank.}
    \label{fig:overlay}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{Figures/DataBankChart.pdf}
  \caption{Structure of the NMRlipids databank. User give information (blue boxes) includes basic information on the simulation, including the location of raw data, as well as experimental data if available. The databank entries (red box) and analysis results (green boxes) then automatically generated by the computer programs included in the NMRlipids databank (yellow boxes).}\label{DatabankStructure}
\end{figure}

Structure of the NMRlipids databank is illustrated in Fig.~\ref{DatabankStructure}. The core of the databank is composed of README.yaml files locating at \url{https://github.com/NMRLipids/Databank/tree/main/Data/Simulations} which contain all the essential information on each simulation entry needed to further applications. As the NMRlipids databank is a overlay databank, the raw simulation data is not stored there but the README.yaml files contain a permanent links to the raw data which can be then accessed when needed. The raw MD simulation data can locate in any stable publicly available repository, although all the current data locates in Zenodo \url{www.zenodo.org}.

A README.yaml file is made using AddData.py script for each simulation stored in the databank based on the information given by the author of the simulation data. In addition to this information, automatically extracted information about the simulation are stored in the README.yaml files (see table~\ref{tab:READMEkeys}). A README.yaml file for each simulation is stored to a folder named according to the hashes of original trajectory and topology file locating in \url{https://github.com/NMRLipids/Databank/tree/main/Data/Simulations}. These README.yaml files give access to all the essential information on the simulations in the databank either directly, or pointing to a original file from where the information can be extracted.

\begin{table}[]
    \centering
    \begin{tabular}{  p{3.5cm}  p{9.5cm}  p{4.0cm} }
    \toprule
    key & description & type  \\
    \midrule
        %\hline
    DOI & DOI from where the raw data is found & user given (compulsory) \\
    SOFTWARE & Software used to run the simulation (e.g. Gromacs, Amber, NAMD, etc.) & \\
    TRJ & Name of the trajectory file found from DOI & \\
    TPR & Name of the topology file found from DOI (trp file in the case of Gromacs) & \\
    PREEQTIME & Pre-equilibrate time simulated before the uploaded trajectory in nanoseconds. \tablefootnote{For example, if you upload 100-200 ns part of total 200 ns simulation, this should value should be 100.} & \\
    TIMELEFTOUT & Equilibration period in the uploaded trajectory that should be discarded in analyses. \tablefootnote{For example, if you upload 0-200 ns part of total 200 ns simulation where the first 100 ns should be considered as an equilibration, this value should be 100.} \\
    COMPOSITION & Molecules names used in the simulation and corresponding mapping files (see ??) & \\
    DIR\_WRK & Temporary working directory in your local computer. \\
    UNITEDATOM\_DICT & Information for constucting hydrogens for united atom simulations, empty for all atom simulations & \\
    TYPEOFSYSTEM & Lipid bilayer or something else & \\
    \hline
    PUBLICATION & Give reference to a publication(s) related to the data. \\
    AUTHORS\_CONTACT & Name and email of the main author(s) of the data. & \\
    SYSTEM & System description on free text format & \\
    SOFTWARE\_VERSION & Version of the used software & \\
    FF & Name of the used force field & \\
    FF\_SOURCE & Source of the force field parameters, e.g, CHARMM-GUI, webpage, citation to a publication, etc. & \\
    FF\_DATE &  Date when force field parameters were accessed on the gives source (day/month/year). & \\
    FF{molename} & Molecule specific force field information, e.g., water model with FFSOL and sodium parameters with FFSOD. & \\
    CPT & Name of the Gromacs checkpoint file. & \\
    LOG & Name of the Gromacs log file. & \\
    TOP & Name of the Gromacs top file. & \\
    GRO & Name of the Gromacs gro file. & \\
    \hline
    TRAJECTORY\_SIZE & Size of the trajectory file in bytes & automatically extracted data. \\
    TRJLENGTH & Lenght of the trajectory (ps). & \\
    TEMPERATURE & Temperature of the simulation. & \\
    NUMBER\_OF\_ATOMS & Number of atoms in the simulation. & \\
    DATEOFRUNNIG & Date when added into the databank & \\
    EXPERIMENT & Potentially connected experimental data & \\
    COMPOSTION & Number of molecules (number of lipids in both leaflets separartely) extracted from the simulation data & \\ 
    \end{tabular}
    \caption{Keys stored in the README.yaml files of simulations.}
    \label{tab:READMEkeys}
\end{table}

Each simulation is connected to the experimental C-H bond order parameter and x-ray scattering form factor data using the searchDATABANK.py script. Available experimental data is collected to \url{https://github.com/NMRLipids/Databank/tree/main/Data/experiments} where each dataset is saved into a folder with the name based on DOI of the related publication and experimental conditions are described in README.yaml files with the keys listed in table~\ref{tab:READMEkeysEXP}. If molar concentrations of all molecules are within $\pm$5 percentage units, charged lipids have the same counterions, and temperature is within $\pm$2 degrees, a pair will be formed between simulation and experimental datasets by adding the link to the experimental data to the simulation README.yaml file. 
%If lipid to water ratio is above ??, the systems are considered fully hydrated. Otherwise also hydration level is considered.

@@

@@

Quality of lipid conformational ensembles are evaluated against C-H bond order parameters from NMR experiments~\cite{ollila16}. As a first step, the quality of each order parameter is evaluated using the negative logarithm of probability to find the simulated order parameter within the experimental error bars
\begin{equation}
    S_q = -\log_{10}(P),    
\end{equation}
where the probability is calculated from the normal distribution
\begin{equation}\label{gaussian}
    P = \int_{S_{\rm exp}-\Delta S_{\rm exp}}^{S_{\rm exp}+
    \Delta S_{\rm exp}}  \frac{1}{\sigma \sqrt{2\pi}} e^{-\frac{1}{2}(\frac{x-\mu}{\sigma})^2} {\rm d}x.
\end{equation}
$S_{\rm exp}$ and $\Delta S_{\rm exp}$ are experimental order parameter and its error, and $\mu$ and $\sigma$ are the mean order parameter and its standard deviation from simulations. The quality measure $S_q$ approaches to zero when probability for agreement between simulation and experimental results approach one, and increases when simulated and experimental values diverge. The accuracy of $\pm$0.02 is currently assumed for all experimental order parameters~\cite{ollila16}. Because phospholipids sample their conformational ensemble within nanosecond timescale~\cite{ferreira15}, all simulations in the databank would be sufficiently long to sample the realistic conformational phase of individual lipids. However, some force fields exhibit too slow dynamics which leads to large error bars in order parameter values~\cite{antila21a}. Because large error bars widen the gaussian distribution in Eq.~\ref{gaussian} thereby artificially increasing the probability to find the simulated value within experimental error bars, the order parameters with error bars larger than the experimental error 0.02 are not included in the quality evaluation.

@@

\subsection{Analysis of the data in databank}

Index files in the datanbank contain all the essential information to perform analyses from the simulations. Systems under interest can be selected automatically browsing the index files and filtering the desired properties.

Analysis results can be most conveniently stored to a new datanbank with identical indexing as the original databank. The results can be then easily shared and browsed indentically to the original databank.

\subsection{Indexing the simulation data}

%\subsubsection*{AddData.py}
AddData.py is a script that builds a database that contains a dictionary file and analysis data of each simulation. The dictionary file contains information about the simulation. The script also calculates order parameters of all CH bonds of the lipids in the simulation. To add a simulation it must be first uploaded to Zenodo (www.zenodo.org). The trajectory and topology files of the simulation are downloaded to the working directory from Zenodo but these are not saved into the database. To add a simulation to the database the user has to give some essential information about the simulation. This is done by writing a info file (*INFO.yaml) which is passed to AddData.py. 
\newline \\
AddData.py requires GROMACS and MDAnalysis library to be installed.
\newline \\
Run AddData.py as follows:
\newline \\
python3 AddData.py -f exampleINFO.yaml
\newline \\
There is also a script runAddData.sh that can be used to loop over several info files to add many simulations at one go.

%\subsubsection*{Simulation dictionary}
A simulation dictionary contains information about the simulation. Some of the information is provided by the user. The numbers of lipid molecules, solvent and ions are automatically read from the files and so are the simulation temperature and trajectory length. All this information is saved to a file named README.yaml.

\subsubsection{User input}
Dictionary variables defined by the user are listed here. 
The necessary parameters required for the analyses are described first and are marked as ''compulsory''. Then the parameters used to describe the data for further usage and analyses are described.
While only compulsory parameters are required for the databank entry, strong recommendation is that all the possible parameters would be given to maximize the possibilities to upcycle the contributed data.

\subsubsection*{DOI (compulsory)}
Give DOI identity from where the simulation files are located. Current databank works only for the data in Zenodo, but other potential sources are may be implemented in the future. Note that the DOI must point to a specific version of dataset in Zenodo, i.e., DOI pointing to all versions of certain dataset does not work.

\subsubsection*{SOFTWARE (compulsory)}
Give the name of software used to run the simulation. The options are GROMACS, AMBER, NAMD, CHARMM and OPENMM. So far, only simulations run with GROMACS are accepted by the script.

\subsubsection*{TRJ (compulsory)}
Give the name of the trajectory file that is found from the DOI given above.

\subsubsection*{TPR (compulsory)}
Give the name of the file with topology information (tpr file in the case of Gromacs) that is found from the DOI given above.

\subsubsection*{PREEQTIME (compulsory)}
Give the time simulated before the uploaded trajectory in nanoseconds. For example, if you upload 100-200~ns part of total 200~ns simulation, this should value should be 100.

\subsubsection*{TIMELEFTOUT (compulsory)}
Give the time that should be considered as an equilibration period in the uploaded trajectory. Frames before the give time will be discarded in the analysis. For example, if you upload 0-200~ns part of total 200~ns simulation where the first 100~ns should be considered as an equilibration, this value should be 100.

\subsubsection*{Molecule names (compulsory)}
In the databank, each molecule has a unique abbreviation (see table~\ref{tab:abbreviations}). 
You need to give the residue names of these molecules corresponding your simulation.
%The user must also provide the names of the molecules, ions and solvent that are used in the simulation to match the names used by the databank. The names provided by the user must be the same as in the tpr file. 
If atoms in a lipid belong to different residues (typical situation in Amber force fields), give the name of the head group residue here, and add the residue name of each atom to the third column in the mapping file (see below). If your simulation contains molecules that are not yet in the databank, you need to define the abbreviation and add molecules to the lipids\_dict, molecules\_dict, molecule\_numbers\_dict and molecule\_ff\_dict in the AddData.py script, as well as to table~\ref{tab:abbreviations}.

\subsubsection*{MAPPING\_DICT (compulsory)}
For the analysis, we need to know the names of atoms in your system.
These are defined using the mapping file convention introduced in \url{http://nmrlipids.blogspot.com/2015/03/mapping-scheme-for-lipid-atom-names-for.html}, where first column gives the universal atom name, second gives the atom name in force field, and third gives the residue name if not the same for all atoms.
The name of the mapping file for each molecule needs to be given in dictionary format. The dictionary the key is the molecule name (abbreviation listed in table \ref{tab:abbreviations}) and the value is the name of the mapping file. The already existing mapping files can be found from the directory named "mapping\_files". If a mapping file for your molecule(s) do not exist, you need to construct one and add to the "mapping\_files" directory.

@@

\subsubsection*{DIR\_WRK (compulsory)}
Give the path of the working directory in your local computer. The trajectory and topology files will be downloaded to this trajectory, and temporary files created during processing will be stored here.

\subsubsection*{UNITEDATOM\_DICT (compulsory for united atom trajectories)}
Order parameters from united atom simulations are calculated using buildH code (\url{https://github.com/patrickfuchs/buildH}). For united atom simulations, you need to tell how hydrogens are added based on definitions in the dic\_lipids.py dictionary. This is done by giving a dictionary where the key is the molecule name (abbreviation listed in table \ref{tab:abbreviations}) and the value is the correct dictionary key in dic\_lipids.py. If correct dictionary key is not yet found, you need to add to dic\_lipids.py. 
In the case of an all atom simulation, UNITEDATOM is left empty.

\subsubsection*{PUBLICATION}
Give reference to a publication(s) related to the data.

\subsubsection*{AUTHORS\_CONTACT}
Give the name and email of the main author(s) of the data.

\subsubsection*{SYSTEM}
Give description of system in free format. For example ''POPC with cholesterol at 301K''.

\subsubsection*{SOFTWARE\_VERSION}
Give the version of the software used.

\subsubsection*{FF}
Give the name of the force field used used in the simulation.

\subsubsection*{FF\_SOURCE}
Describe the source of the force field parameters. For example, CHARMM-GUI, link to webpage where parameters were downloaded, or citation to a paper.

\subsubsection*{FF\_DATE}
Give the date when parameters were accessed or created. The format is day/month/year.

\subsubsection*{Individual force field names for molecules}
In some cases special force fields are used for certain molecules. For example, non-standard parameters for ions or other molecules have been used. These can be specified giving forcefield names separately for individual molecules. These can be given as parameters named as
FF+[abbreviation from table \ref{tab:abbreviations}], i.e., FFPOPC, FFPOT, FFSOL etc.

\subsubsection*{CPT (Gromacs)}
Give the name of the Gromacs checkpoint file that is found from the DOI given above.
CPT stands for the name of the cpt file.

\subsubsection*{LOG (Gromacs)}
Give the name of the Gromacs log file that is found from the DOI given above.

\subsubsection*{TOP (Gromacs)}
Give the name of the Gromacs top file that is found from the DOI given above.

\subsubsection{Automatically analyzed parameters}
The following parameters are read automatically from the trajectory and topology files.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%automatically analyzed parameters%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Molecule numbers}
Numbers of lipid molecules (NPOPC, NPOPG, etc.) per membrane leaflet are calculated by determining on which side of the center of mass of the membrane the center of mass of the head group of each lipid molecule is located.
\newline \\
\noindent Numbers of other molecules such as solvent and ions (NSOL, NPOT, NSOD, etc.) are read from the topology file.

\subsubsection*{Temperature}
Temperature of the simulation is read from the topology file.

\subsubsection*{Trajectory length}
The length of a trajectory is read from the trajectory file.

\subsubsection*{Date of running}
The date of running the script is saved to the README.yaml file.

>>>>

\begin{figure}
    \centering
    \includegraphics[width = 180mm]{Figures/overlay.pdf}
    \caption{a) Structure of an overlay databank. 
    %Raw data is available from a publicly accessible repository (layer 1).
    %The core of the databank contains information on the location of the raw data and indexing of molecular %compositions and simulation details described with universal naming conventions (layer 2).
    %The content of databank can be viewed and analysed using external programs that automatically read the information and data from layers 1 and 2 (layer 3). Examples of such applications are the GitHub repository generating the results presented in this work and the graphical access to the databank.
    More detailed structure of the layer 2 in the NMRlipids databank is illustrated in Fig.~\ref{DatabankStructure} in the SI.
    b) Distribution of the lengths of the trajectories, total number of trajectories and total lenght of the simulations in the NMRlipids databank.
    c) Distribution of lipids present in the trajectories in the NMRlipids databank. Lipids occuring in five or less simulations ('others') are listed in the right. 
    d) Currently available binary mixtures in the NMRlipids databank. 
    e) Distribution of force fields in the simulations in the NMRlipids databank.
    The figures and numbers are created on 9th of May 2022.}
    \label{fig:overlay}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{Figures/DataBankChart.pdf}
  \caption{Structure of the NMRlipids databank. Manually added input data (blue boxes) includes basic information on the simulation, permanent links to the raw data, and experimental data if available. The databank entries (red box) and analysis results (green boxes), locating at \url{https://github.com/NMRLipids/Databank/tree/main/Data/Simulations} are automatically generated by the computer programs included in the NMRlipids databank (yellow boxes). Because raw data are not permanently stored but can be accessed based on the information in the databank, this connection is marked with the dashed line. }\label{DatabankStructure}
\end{figure}

Structure of the NMRlipids databank is illustrated in Fig.~\ref{DatabankStructure}. The required input information to create an entry into the NMRlipids databank are listed in table~\ref{tab:READMEkeys}. While the raw simulation data is not directly stored in the NMRlipids databank, permanent links from where the raw data can be accessed have to be given and are then stored in the README.yaml files at \url{https://github.com/NMRLipids/Databank/tree/main/Data/Simulations}. These files contain all the essential information listed in table~\ref{tab:READMEkeys} on each simulation entry that are needed for further applications. The raw MD simulation data can locate in any stable publicly available repository, although all the current data locates in Zenodo \url{www.zenodo.org}.

%A README.yaml file is made using AddData.py script for each simulation stored in the databank based on the information given by the author of the simulation data. In addition to this information, automatically extracted information about the simulation are stored in the README.yaml files (see table~\ref{tab:READMEkeys}). A README.yaml file for each simulation is stored to a folder named according to the hashes of original trajectory and topology file locating in \url{https://github.com/NMRLipids/Databank/tree/main/Data/Simulations}. These README.yaml files give access to all the essential information on the simulations in the databank either directly, or pointing to a original file from where the information can be extracted.

\begin{table}[]
    \centering
    \begin{tabular}{  p{3.5cm}  p{9.5cm}  p{4.0cm} }
    \toprule
    key & description & type  \\
    \midrule
        %\hline
    DOI & DOI from where the raw data is found & user given (compulsory) \\
    SOFTWARE & Software used to run the simulation (e.g. Gromacs, Amber, NAMD, etc.) & \\
    TRJ & Name of the trajectory file found from DOI & \\
    TPR & Name of the topology file found from DOI (trp file in the case of Gromacs) & \\
    PREEQTIME & Pre-equilibrate time simulated before the uploaded trajectory in nanoseconds. \tablefootnote{For example, if you upload 100-200 ns part of total 200 ns simulation, this should value should be 100.} & \\
    TIMELEFTOUT & Equilibration period in the uploaded trajectory that should be discarded in analyses. \tablefootnote{For example, if you upload 0-200 ns part of total 200 ns simulation where the first 100 ns should be considered as an equilibration, this value should be 100.} \\
    COMPOSITION & Molecules names used in the simulation and corresponding mapping files (see ??) & \\
    DIR\_WRK & Temporary working directory in your local computer. \\
    UNITEDATOM\_DICT & Information for constucting hydrogens for united atom simulations, empty for all atom simulations & \\
    TYPEOFSYSTEM & Lipid bilayer or something else & \\
    \hline
    PUBLICATION & Give reference to a publication(s) related to the data. & User given (optional)\\
    AUTHORS\_CONTACT & Name and email of the main author(s) of the data. & \\
    SYSTEM & System description on free text format & \\
    SOFTWARE\_VERSION & Version of the used software & \\
    FF & Name of the used force field & \\
    FF\_SOURCE & Source of the force field parameters, e.g, CHARMM-GUI, webpage, citation to a publication, etc. & \\
    FF\_DATE &  Date when force field parameters were accessed on the gives source (day/month/year). & \\
    FF{molename} & Molecule specific force field information, e.g., water model with FFSOL and sodium parameters with FFSOD. & \\
    CPT & Name of the Gromacs checkpoint file. & \\
    LOG & Name of the Gromacs log file. & \\
    TOP & Name of the Gromacs top file. & \\
    GRO & Name of the Gromacs gro file. & \\
    \hline
    TRAJECTORY\_SIZE & Size of the trajectory file in bytes & automatically extracted data. \\
    TRJLENGTH & Lenght of the trajectory (ps). & \\
    TEMPERATURE & Temperature of the simulation. & \\
    NUMBER\_OF\_ATOMS & Number of atoms in the simulation. & \\
    DATEOFRUNNIG & Date when added into the databank & \\
    EXPERIMENT & Potentially connected experimental data & \\
    COMPOSITION & Numbers of lipid molecules (NPOPC, NPOPG, etc.) per membrane leaflet are calculated by determining on which side of the center of mass of the membrane the center of mass of the head group of each lipid molecule is located.
    Numbers of other molecules such as solvent and ions (NSOL, NPOT, NSOD, etc.) are read from the topology file. & \\
    \end{tabular}
    \caption{Keys stored in the README.yaml files of simulations.}
    \label{tab:READMEkeys}
\end{table}

In order to evaluate the quality of simulations, sets of C-H bond order parameters from NMR and from factors from x-ray scattering are included in the NMRlipids databank (\url{https://github.com/NMRLipids/Databank/tree/main/Data/experiments}). The required information for an experimental dataset are listed in table~\ref{tab:READMEkeysEXP}.
A simulation is connected to a experimental data set
%C-H bond order parameter and x-ray scattering form factor data using the searchDATABANK.py script. Available experimental data is collected to  where each dataset is saved into a folder with the name based on DOI of the related publication and experimental conditions are described in README.yaml files with the keys listed in table~\ref{tab:READMEkeysEXP}. 
if molar concentrations of all molecules are within $\pm$5 percentage units, charged lipids have the same counterions, and temperature is within $\pm$2 degrees. In such cases, a simulation and experimental data are paired by adding the path to the experimental data into the simulation README.yaml file. 
%If lipid to water ratio is above ??, the systems are considered fully hydrated. Otherwise also hydration level is considered.

@@

Because README.yaml contains all the essential information on each simulation, arbitrary analyses can be automatically performed over all the simualtions in the NMRlipids databank. In addition to the order parameters for each C-bonds and x-ray scattering form factors used in the quality evaluation, the NMRlipids databank contains the area per lipid and thickness calculated from all simulations in the databank. These results are stored in the same folders as the README.yaml files in \url{https://github.com/NMRLipids/Databank/tree/main/Data/Simulations}.

\subsection{Molecule and atom naming convention}

Because universal convention for lipid molecules and atoms therein has not been defined, the naming conventions vary between authors and force fields. To enable automatic analyses over large sets of simulation in the NMRlipids databank, we have defined unique naming conventions for lipid molecules and atoms. The abbreviations of molecule names used in the NMRlipids databank are listed in table~\ref{tab:abbreviations}. The unique atom names for each molecule and corresponding names in each simulation are defined using mapping files introduced in the NMRlipids project (\url{https://nmrlipids.blogspot.com/2022/04/new-yaml-format-of-mapping-files.html}).

Molecule and atom names in each simulation are connected to the unique naming convention with the COMPOSITION dictionary in the README.yaml file. Upon addition of a new entry in the databank, the molecule names in the simulation corresponding the unique names and mapping files (available at \url{https://github.com/NMRLipids/Databank/tree/main/Scripts/BuildDatabank/mapping_files}) are defined in the dictionary. The numbers of molecules in the system are then automatically calculated by the NMRlipids databank codes (AddData.py in Fig.~\ref{DatabankStructure}) and stored in the README.yaml together with other content of the COMPOSITION dictionary. This information can be then used to find each molecule and atom from each simulation in the analysis codes.

@@

Quality of conformational ensembles of lipid molecules in simulations are evaluated by estimating the average probability of C-H bond order parameters to agree with the values from NMR experiments. 
%As a first step, the quality of each order parameter is evaluated using the negative logarithm of probability to find the simulated order parameter within the experimental error bars
%\begin{equation}
%    S_q = -\log_{10}(P),    
%\end{equation}
Because each C-H bond order parameter is calculated as an average over individual lipids in a simulation and conformational ensembles of lipids are assumed to be independent, the random variable
\begin{equation}
    \frac{\bar{X}-\mu}{S/\sqrt{n}},
\end{equation}
where $\bar{X}$ is the sample mean, $S$ is the sample variance and $n$ is the sample size (number of lipids), has a Student's t-distribution with $n-1$ degrees of freedom and the mean of $\mu$.

where the probability is calculated from the normal distribution
\begin{equation}\label{gaussian}
    P = \int_{S_{\rm exp}-\Delta S_{\rm exp}}^{S_{\rm exp}+
    \Delta S_{\rm exp}}  \frac{1}{\sigma \sqrt{2\pi}} e^{-\frac{1}{2}(\frac{x-\mu}{\sigma})^2} {\rm d}x.
\end{equation}
$S_{\rm exp}$ and $\Delta S_{\rm exp}$ are experimental order parameter and its error, and $\mu$ and $\sigma$ are the mean order parameter and its standard deviation from simulations. The quality measure $S_q$ approaches to zero when probability for agreement between simulation and experimental results approach one, and increases when simulated and experimental values diverge. The accuracy of $\pm$0.02 is currently assumed for all experimental order parameters~\cite{ollila16}. Because phospholipids sample their conformational ensemble within nanosecond timescale~\cite{ferreira15}, all simulations in the databank would be sufficiently long to sample the realistic conformational phase of individual lipids. However, some force fields exhibit too slow dynamics which leads to large error bars in order parameter values~\cite{antila21a}. Because large error bars widen the gaussian distribution in Eq.~\ref{gaussian} thereby artificially increasing the probability to find the simulated value within experimental error bars, the order parameters with error bars larger than the experimental error 0.02 are not included in the quality evaluation.

@@

\subsection{Analysing simulations in the NMRlipids databank}

The README.yaml files contain all the essential information to perform arbitrary analyses of simulations in the NMRlipids databank, i.e., the permanent location of the original data and naming convention for all atoms and molecules in each system. In practise, the analyse codes contains a loop over all README.yaml files (i.e., simulations in the NMRlipids databank) which first downloads the raw simulation to a local computer and then uses the information about the atom and molecule naming conventions in README.yaml and mapping files to perform the desired analyses. For example, the code that calculates all C-H bond order parameters of all systems is available at \url{https://github.com/NMRLipids/Databank/blob/main/Scripts/AnalyzeDatabank/calcOrderParameters.py} and minimal example of a analysis code is available at \url{https://github.com/NMRLipids/Databank/blob/main/Scripts/AnalyzeDatabank/template.ipynb}.

While the order parameters, form factors, area per lipid and thickness are stored within the NMRlipids databank (\url{https://github.com/NMRLipids/Databank/tree/main/Data/Simulations}), further analyses can be conventiently stored in separate repositories with the same folder structure based on hash identities of trajectory and topology files. For example, results from further analyses performed here are stored in folders at \url{https://github.com/NMRLipids/DataBankManuscript/tree/main/Data}. Such organization of the data enables further upcycling of the analyzed data as similarly to the original NMRlipids databank repository.

%\subsection{Indexing the simulation data}

%\subsubsection*{AddData.py}
%AddData.py is a script that builds a database that contains a dictionary file and analysis data of each simulation. The dictionary file contains information about the simulation. The script also calculates order parameters of all CH bonds of the lipids in the simulation. To add a simulation it must be first uploaded to Zenodo (www.zenodo.org). The trajectory and topology files of the simulation are downloaded to the working directory from Zenodo but these are not saved into the database. To add a simulation to the database the user has to give some essential information about the simulation. This is done by writing a info file (*INFO.yaml) which is passed to AddData.py. 
%\newline \\
%AddData.py requires GROMACS and MDAnalysis library to be installed.
%\newline \\
%Run AddData.py as follows:
%\newline \\
%python3 AddData.py -f exampleINFO.yaml
%\newline \\
%There is also a script runAddData.sh that can be used to loop over several info files to add many simulations at one go.

%\subsubsection*{Simulation dictionary}
%A simulation dictionary contains information about the simulation. Some of the information is provided by the user. The numbers of lipid molecules, solvent and ions are automatically read from the files and so are the simulation temperature and trajectory length. All this information is saved to a file named README.yaml.

%\subsubsection{User input}
%Dictionary variables defined by the user are listed here. 
%The necessary parameters required for the analyses are described first and are marked as ''compulsory''. Then the parameters used to describe the data for further usage and analyses are described.
%While only compulsory parameters are required for the databank entry, strong recommendation is that all the possible parameters would be given to maximize the possibilities to upcycle the contributed data.

%\subsubsection*{DOI (compulsory)}
%Give DOI identity from where the simulation files are located. Current databank works only for the data in Zenodo, but other potential sources are may be implemented in the future. Note that the DOI must point to a specific version of dataset in Zenodo, i.e., DOI pointing to all versions of certain dataset does not work.

%\subsubsection*{SOFTWARE (compulsory)}
%Give the name of software used to run the simulation. The options are GROMACS, AMBER, NAMD, CHARMM and OPENMM. So far, only simulations run with GROMACS are accepted by the script.

%\subsubsection*{TRJ (compulsory)}
%Give the name of the trajectory file that is found from the DOI given above.

%\subsubsection*{TPR (compulsory)}
%Give the name of the file with topology information (tpr file in the case of Gromacs) that is found from the DOI given above.

%\subsubsection*{PREEQTIME (compulsory)}
%Give the time simulated before the uploaded trajectory in nanoseconds. For example, if you upload 100-200~ns part of total 200~ns simulation, this should value should be 100.

%\subsubsection*{TIMELEFTOUT (compulsory)}
%Give the time that should be considered as an equilibration period in the uploaded trajectory. Frames before the give time will be discarded in the analysis. For example, if you upload 0-200~ns part of total 200~ns simulation where the first 100~ns should be considered as an equilibration, this value should be 100.

%\subsubsection*{Molecule names (compulsory)}
%In the databank, each molecule has a unique abbreviation (see table~\ref{tab:abbreviations}). 
%You need to give the residue names of these molecules corresponding your simulation.
%The user must also provide the names of the molecules, ions and solvent that are used in the simulation to match the names used by the databank. The names provided by the user must be the same as in the tpr file. 
%If atoms in a lipid belong to different residues (typical situation in Amber force fields), give the name of the head group residue here, and add the residue name of each atom to the third column in the mapping file (see below). If your simulation contains molecules that are not yet in the databank, you need to define the abbreviation and add molecules to the lipids\_dict, molecules\_dict, molecule\_numbers\_dict and molecule\_ff\_dict in the AddData.py script, as well as to table~\ref{tab:abbreviations}.

%\subsubsection*{MAPPING\_DICT (compulsory)}
%For the analysis, we need to know the names of atoms in your system.
%These are defined using the mapping file convention introduced in \url{http://nmrlipids.blogspot.com/2015/03/mapping-scheme-for-lipid-atom-names-for.html}, where first column gives the universal atom name, second gives the atom name in force field, and third gives the residue name if not the same for all atoms.
%The name of the mapping file for each molecule needs to be given in dictionary format. The dictionary the key is the molecule name (abbreviation listed in table \ref{tab:abbreviations}) and the value is the name of the mapping file. The already existing mapping files can be found from the directory named "mapping\_files". If a mapping file for your molecule(s) do not exist, you need to construct one and add to the "mapping\_files" directory.

@@

%\subsubsection*{DIR\_WRK (compulsory)}
%Give the path of the working directory in your local computer. The trajectory and topology files will be downloaded to this trajectory, and temporary files created during processing will be stored here.

%\subsubsection*{UNITEDATOM\_DICT (compulsory for united atom trajectories)}
%Order parameters from united atom simulations are calculated using buildH code (\url{https://github.com/patrickfuchs/buildH}). For united atom simulations, you need to tell how hydrogens are added based on definitions in the dic\_lipids.py dictionary. This is done by giving a dictionary where the key is the molecule name (abbreviation listed in table \ref{tab:abbreviations}) and the value is the correct dictionary key in dic\_lipids.py. If correct dictionary key is not yet found, you need to add to dic\_lipids.py. 
%In the case of an all atom simulation, UNITEDATOM is left empty.

%\subsubsection*{PUBLICATION}
%Give reference to a publication(s) related to the data.

%\subsubsection*{AUTHORS\_CONTACT}
%Give the name and email of the main author(s) of the data.

%\subsubsection*{SYSTEM}
%Give description of system in free format. For example ''POPC with cholesterol at 301K''.

%\subsubsection*{SOFTWARE\_VERSION}
%Give the version of the software used.

%\subsubsection*{FF}
%Give the name of the force field used used in the simulation.

%\subsubsection*{FF\_SOURCE}
%Describe the source of the force field parameters. For example, CHARMM-GUI, link to webpage where parameters were downloaded, or citation to a paper.

%\subsubsection*{FF\_DATE}
%Give the date when parameters were accessed or created. The format is day/month/year.

%%\subsubsection*{Individual force field names for molecules}
%In some cases special force fields are used for certain molecules. For example, non-standard parameters for ions or other molecules have been used. These can be specified giving forcefield names separately for individual molecules. These can be given as parameters named as
%FF+[abbreviation from table \ref{tab:abbreviations}], i.e., FFPOPC, FFPOT, FFSOL etc.

%\subsubsection*{CPT (Gromacs)}
%Give the name of the Gromacs checkpoint file that is found from the DOI given above.
%CPT stands for the name of the cpt file.

%\subsubsection*{LOG (Gromacs)}
%Give the name of the Gromacs log file that is found from the DOI given above.

%\subsubsection*{TOP (Gromacs)}
%Give the name of the Gromacs top file that is found from the DOI given above.

%\subsubsection{Automatically analyzed parameters}
%The following parameters are read automatically from the trajectory and topology files.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%automatically analyzed parameters%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\subsubsection*{Molecule numbers}
%Numbers of lipid molecules (NPOPC, NPOPG, etc.) per membrane leaflet are calculated by determining on which side of the center of mass of the membrane the center of mass of the head group of each lipid molecule is located.
%\newline \\
%\noindent Numbers of other molecules such as solvent and ions (NSOL, NPOT, NSOD, etc.) are read from the topology file.

%\subsubsection*{Temperature}
%Temperature of the simulation is read from the topology file.

%\subsubsection*{Trajectory length}
%The length of a trajectory is read from the trajectory file.

%\subsubsection*{Date of running}
%The date of running the script is saved to the README.yaml file.
